Something about correlation functions

### 2021-07-07 paper-correlations.tex
Change few words

To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: Nvidia GeForce GTX 1650 with 4~Gb video memory
\end{itemize}

We generate two (resp. three) dimensional square (resp. cubic) binary arrays
with different number of elements. The arrays are filled with thresholded value
noise using \code{ValueNoise.jl} package and this code:
\begin{verbatim}
using ValueNoise

getdata(side, dims :: Integer) =
    getdata(side, Val(dims))

getdata(side, :: Val{2}) =
    [value_noise(5x/side,
                 5y/side,
                 0.0,
                 5, 34365) < 0.5
     for x in 1:side, y in 1:side]

getdata(side, :: Val{3}) =
    [value_noise(5x/side,
                 5y/side,
                 5z/side,
                 5, 34365) < 0.5
     for x in 1:side, y in 1:side, z in 1:side]
\end{verbatim}
An example of a two-dimensional image generated in this way is on
\cref{fig:valuenoise}. The function \code{getdata} generates the same image
sampled with different resolutions.

@@

To measure efficiency of \code{Map} module we follow the same procedure but with
seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
cubes with a side $s = 50, 100, \dots, 350$ voxels. The surface-void correlation
functions on \cref{fig:timings-2d-gpu} and \cref{fig:timings-3d-gpu} are
calculates with a lesser number of sides because it's too demanding in video
memory.

Also many functions in \code{Map} module can utilize Nvidia's GPUs using the
CUDA library. For example, two-point correlation function uses FFT transform
optimized for Nvidia GPUs and provided in \code{CUDA.FFT} package. The choice
between CPU or GPU version is made depending on type of input array. If it's
\code{CuArray} rather than generic \code{AbstractArray} then CUDA implementation
is chosen.

The measurements of execution time is on \cref{fig:timings}. As you can see, GPU
versions (when available) are faster than CPU versions and limited only by
amount of video memory. Functions in \code{Directional} are slower (with
exception of the lineal-path function) but are also useful in media
reconstruction algorithms which utilize simulated annealing.

>>>>

To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: Nvidia Tesla V100 with 32~Gb video memory
\end{itemize}

We generate two (resp. three) dimensional square (resp. cubic) binary arrays
with different number of elements. Each element $a_{ij}$ (resp. $a_{ijk}$) of a
two-dimensional (resp. three-dimensional) array is calculated as follows:
\begin{align*}
  a_{ij} & = \left\{
  \begin{array}{ll}
    0 & \quad vn(5i/s, 5j/s, 0, 5, 34365) < 0.5 \\
    1 & \quad \text{otherwise}
  \end{array}
  \right. \\
  a_{ijk} & = \left\{
  \begin{array}{ll}
    0 & \quad vn(5i/s, 5j/s, 5k/s, 5, 34365) < 0.5 \\
    1 & \quad \text{otherwise}
  \end{array}
  \right.
\end{align*}
Here $vn(x,y,z,o,s)$ is a value noise function. We fix a number of
octaves $o = 5$ and a random seed $s = 34365$. The particular implementation for
our measurements was taken from \code{ValueNoise.jl} package. An example of a
two-dimensional image generated in this way is on \cref{fig:valuenoise}.

@@

With the \code{Map} module we follow the same procedure. Many functions in
\code{Map} can utilize Nvidia's GPUs using the CUDA library. For example,
two-point correlation function uses FFT transform optimized for Nvidia GPUs and
provided in \code{CUDA.FFT} package. We provide execution times for bot CPU and
GPU. The choice between CPU or GPU version is made depending on type of input
array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
implementation is chosen.

The measurements of execution time is on \cref{fig:timings}. As you can see, GPU
versions (when available) are faster than CPU versions and limited only by
amount of video memory. Functions in \code{Directional} are slower (with
exception of the lineal-path function) but are also useful in medium
reconstruction algorithms which utilize simulated annealing.
